---
title: "Case_Study_2"
author: "Ben Tanaka"
date: "7/29/2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, echo=FALSE, include=FALSE, warning=FALSE,message =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE,message =FALSE)
library(xml2)
library(rvest)
library(stringr)
library(tibble)
library(data.table)
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(bizdays)
library(MTS)
library(forecast)
library(smooth)
library(fpp2)
library(lubridate)
library(dygraphs)
library(xts)
library(readxl)
library(tidyverse)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
library(GGally)

setwd("/users/ben/documents/r/Case_Study_2")
getwd()
```

# DDSAnalytics:  Predicting Employee Turnover

```{r ETL}
df_emp_ren <- read_excel("CaseStudy2-data.xlsx")
names(df_emp_ren)

df_emp_ren$Attrition_Lvl <- factor(df_emp_ren$Attrition)
str(df_emp_ren)
summary(df_emp_ren)

```


## Employee Personal Demographics
``` {r Employee_Demographics}
EmpPerDem1 <- df_emp_ren[c("EducationField","Education","Attrition_Lvl")]
ggpairs(EmpPerDem1)

EmpPerDem2 <- df_emp_ren[c("NumCompaniesWorked","TotalWorkingYears", "DistanceFromHome" ,"Attrition_Lvl")]
ggpairs(EmpPerDem2)

EmpPerDem3 <- df_emp_ren[c("MaritalStatus","Gender","Over18","Age","Attrition_Lvl")]
ggpairs(EmpPerDem3)

```

### Employee Personal Demographics:  Insights
* Insights:
    1.  enter insights here
      + Hypothesis: 


## Employee Pay Rates
``` {r Employee Pay Rates}
EmpPayRte1 <- df_emp_ren[c("HourlyRate", "DailyRate", "MonthlyRate","MonthlyIncome", "PercentSalaryHike","Attrition_Lvl")]
ggpairs(EmpPayRte1)

EmpPayRte2 <- df_emp_ren[c("StockOptionLevel","OverTime","Attrition_Lvl")]
ggpairs(EmpPayRte2)

```

### Employee Pay Rates:  Insights
* Insights:
    1.  enter insights here
      + Hypothesis: 

## Employee Work Profile Demographics
```{r Employee Work Profile Demographics}
EmpPflDem1 <- df_emp_ren[c("YearsWithCurrManager","YearsSinceLastPromotion","YearsInCurrentRole","YearsAtCompany","PerformanceRating", "Attrition_Lvl")]
ggpairs(EmpPflDem1)

EmpPflDem2 <- df_emp_ren[c("WorkLifeBalance","RelationshipSatisfaction","JobSatisfaction","JobInvolvement","EnvironmentSatisfaction", "Attrition_Lvl")]
ggpairs(EmpPflDem2)

EmpPflDem3 <- df_emp_ren[c("TrainingTimesLastYear","StandardHours","JobRole","JobLevel","Department","BusinessTravel", "Attrition_Lvl")]
ggpairs(EmpPflDem3)

EmpPflDem4 <- df_emp_ren[c("YearsAtCompany", "YearsInCurrentRole", "YearsSinceLastPromotion","YearsWithCurrManager", "Attrition_Lvl")]
ggpairs(EmpPflDem4)

```

### Employee Work Profile Demographics:  Insights
* Insights:
    1.  enter insights here
      + Hypothesis: 